### 2018-05-02 paper/evaluation.tex
eval

% \subsection{Devices' predictions of the user behavior} % (fold)
% \label{sub:devices_predictions_of_the_user_behavior}

% Adios, section

%\commentAL{Should evaluate the inference of the model given only the observable sequence. Also show that $P[O_{t+1} | S_t] \simeq P[O_{t+i} | S_t]$}

>>>>

\paragraph*{File exchange}
In section~\ref{sub:file_transfer}, we fix the routes' creation parameters: $\theta=10^-3$, $L=3$.
The number of users is set to 20, and the number of file exchange per experiment to 10.
We use a constant file chunk size of 512kB, a constant header size of 100kB, and a constant bandwidth per link of 128kB/s.
